\section{2018-02-14}

\subsection{Dynamic Memory}

Some points:

\begin{itemize}
  \item Objects are allocated by a call to \cpp{new} and dellocated by a call to \cpp{delete}.
  \item Objects are created as the program needs them.
  \item So, there needs to be no relationship between dynamic memory and variables - known at compile time.
  \item \cpp{new} will invoke the appropriate constructor.
  \item New arrays of objects requrie a default constructor.
\end{itemize}

Upside of dynamic memory: \textbf{flexibility}. Downside: \textbf{memory management}.

Construction:

\begin{lstlisting}[language=C++]
int* p = new int;
int* q = new int[/* ? size */];
\end{lstlisting}

Destruction: Always a call to new with \underline{an appropriate} call to \cpp{delete}.

\begin{lstlisting}[language=C++]
delete p;
delete[] q;
\end{lstlisting}

Bad deletions \textrightarrow B I G   P R O B L E M S

\subsection{Dangling pointers}

\subsubsection{Shallow copies}

Shallow copies - Copying a pointer instead of what it points to. Deleting both, you have a ``double delete''.

Fix: write your own copy constructor and assignment operator

\begin{lstlisting}[language=C++]
class bad {
  public:
    bad() { p = new int(0); }
    ~bad() { delete p; }
    int* p;
};

//...

void f() {
  bad a;
  bad b = a;
  //...
}
\end{lstlisting}

What happens...? When control leaves the scope of \cpp{f()}, we got a double delete. Here's an alternative:

\begin{lstlisting}[language=C++]
class good {
  public:
    good() { p = new int(0); }
    ~good() { delete p; }
    good(const good& s) : p(new int(*s.p)) { }
    
    good& operator=(const good& s) {
      if (s.p != p) {
        delete p;
        p = new int(*s.p);
      }
      return *this;
    }
    
    int* p;
};
\end{lstlisting}

\subsubsection{Setting a poniter to an automatic object}

When the object goes out of scope, the pointer points to nothing.

FIx: Don't point to automatic objects.

\subsubsection{Deleting a function parameter}

Suppose you pass a pointer to function and delete it there? In the calling function the pointer is useless.

Fix: Don't do this - don't delete function parameters.

\subsubsection{Garbage}

Use smart pointers.

\subsection{The Story}

(Paraphrased)

``I don't know if I have time, but I've got to tell you this story. I've lived a long time and I've lived through a bunch of crazy shit in my life. In 1983, before this event, medicine packaging did not have as many layers as it did today: Someone had gone and injected extra-strength Tylenol into a bunch of packages of medicine. That semester, before a test, one of my students got up and set an apple on my desk - everyone chuckled a bit. He went on to fail the test, and after he did, he then set a little package on the desk. It was Tylenol, but the guy had scratched onto the label, `Extra-Strength' next to `Tylenol', which everyone thought was pretty funny. Nowadays, that kid would get in huge trouble and get sued and everything, but back then I just thought it was pretty darn funny.''

In the middle of telling this story, he told another story of his friends leaving another one of his friends who was to be married the next day on a train car. He woke up the next day in Oklahoma City.

\subsection{Curves}

Lagrange form = Newtwon form

\begin{equation}
  P_N(x) = a_0 + a_1 (x - x_0) + a_2 (x - x_1) (x - x_0) + ... + a_N (x - x_{N-1}) ... (x - x_0)
\end{equation}

Where $a_k = f[x_0, x_1, x_2, ..., x_k]; k = 0, 1, ..., N$

f[]:

\begin{align*}
  f[x_k]                   &= f(x_k) = y_k \\
  f[x_{k-1}, x_k]          &= \frac{f[x_k] - f[x_{k-1}]}{x_k - x_{k-1}} \\
  f[x_{k-2}, x_{k-1}, x_k] &= \frac{f[x_{k-1}, x_k] - f[x_{k-2}, x_{k-1}]}{x_k - x_{k-2}}
\end{align*}

\underline{The Table:}

\begin{tabular}{ |c|c|c|c|c| }
$x_k$ & $y_k$ & $f[,]$        & $f[,,]$            & $f[,,,]$\\
\hline
$x_0$ & $y_0$ & -             & -                  & - \\
$x_1$ & $y_1$ & $f[x_0, x_1]$ & -                  & - \\
$x_2$ & $y_2$ & $f[x_1, x_2]$ & $f[x_0, x_1, x_2]$ & - \\
$x_3$ & $y_3$ & $f[x_2, x_3]$ & $f[x_1, x_2, x_3]$ & $f[x_0, x_1, x_2, x_3]$
\end{tabular}